NEW TITLE

### 2019-11-04 paper.tex
Moved Delta_f to other section

\subsubsection{Pitch Discrimination} \label{sec:pitch_discrimination}

@@

The first tone is randomly generated, while the second tone is generated by adding or subtracting some value from the first one.
The tone difference depends on how well the participant can tell the tones apart.
Like the sound localisation experiment, a ``2-up, 1-down'' step process is used: for every two consecutive correct answers, the pitch difference between the tones is halved, while it is doubled for every incorrect answer.
Two-step sequences are again used here, one starting with a large pitch difference ($f_h=2^9=$ \SI{512}{\hertz}) between the tones and the other with a small difference ($f_l=2^1=$ \SI{2}{\hertz}).
The termination condition is when the two-step sequences are within one octave of each other (i.e.\ $\log_2\frac{f_h}{f_l}=2$) for three consecutive answers.
For example, the experiment will terminate when one sequence is set to \SI{64}{\hertz} and the other is between \SI{32}{\hertz} or \SI{128}{\hertz} for three consecutive guesses.
Each participant performed this experiment twice.

\subsection{Target Search} \label{sec:target_search}

@@

Group \textit{G2} also displays a concentration of erroneous guesses in the central interval.
However, it also shows more errors in other distance intervals and a more even progression towards the centre.
This could indicate that, instead of terminating the experiment by bringing the two sequences within one interval of one another \tofix{I would just say ``terminating the experiment as explained in Sec.~\ref{sec:sound_localisation}'', but then there you said within two intervals, not one...}, there was more switching back and forth between the three central intervals.

@@

The results of the pitch discrimination experiment are shown in \Cref{fig:pitch-discrimination}, where bar plots are used to show the proportion of correct to incorrect guesses of which tone was higher pitched for different tone difference intervals. 
\tofix{The $\Delta f$ explanation should be moved to Sec.~\ref{sec:pitch_discrimination}}
The latter is given in terms of semitone-differences which is obtained with

\begin{equation}
\label{eq:semitone-difference}
  \Delta f = 12\log_2\frac{f_0}{f_1}.
\end{equation}

For Group \textit{G1}, we see that their guesses are normally spread around the 0 semitone-difference interval and, as expected, the highest proportion of incorrect guesses occurs in the $[-0.25, 0.25]$ semitone-difference interval. 
The guesses from Group \textit{G2} are more concentrated around the centre and the majority of incorrect guesses also occurs in the $[-0.25, 0.25]$ semitone-difference interval.

>>>>

\subsubsection{Pitch Discrimination}\label{sec:pitch_discrimination}

@@

The first tone is randomly generated, while the second tone is generated by adding or subtracting some value from the first one.
The tone difference depends on how well the participant can tell the tones apart.
Like the sound localisation experiment, a ``2-up, 1-down'' step process is used: for every two consecutive correct answers, the pitch difference between the tones is halved, while it is doubled for every incorrect answer.
Two-step sequences are again used here, one starting with a large pitch difference ($f_h=2^9=$ \SI{512}{\hertz}) between the tones and the other with a small difference ($f_l=2^1=$ \SI{2}{\hertz}).
The termination condition is when the two-step sequences are within one octave of each other (i.e.\ $\log_2\frac{f_h}{f_l}=2$) for three consecutive answers.
For example, the experiment will terminate when one sequence is set to \SI{64}{\hertz} and the other is between \SI{32}{\hertz} or \SI{128}{\hertz} for three consecutive guesses.
Pitch differences are measured in semitones, which can be obtained with

\begin{equation}
\label{eq:semitone-difference}
  \Delta f = 12\log_2\frac{f_0}{f_1}, 
\end{equation}

\noindent where $f_0$ and $f_1$ are the frequencies of the first and second tone respectively.
Each participant performed this experiment twice.

\subsection{Target Search}\label{sec:target_search}

@@

Group \textit{G2} also displays a concentration of erroneous guesses in the central interval.
However, it also shows more errors in other distance intervals and a more even progression towards the centre.
This could indicate that, instead of terminating the experiment as described in \cref{sec:sound_localisation}, there was more switching back and forth between the three central intervals.

@@

The results of the pitch discrimination experiment are shown in \Cref{fig:pitch-discrimination}, where bar plots are used to show the proportion of correct to incorrect guesses of which tone was higher pitched for different tone difference intervals. 
For Group \textit{G1}, we see that their guesses are normally spread around the 0 semitone-difference interval and, as expected, the highest proportion of incorrect guesses occurs in the $[-0.25, 0.25]$ semitone-difference interval. 
The guesses from Group \textit{G2} are more concentrated around the centre and the majority of incorrect guesses also occurs in the $[-0.25, 0.25]$ semitone-difference interval.
